Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-05 lineages_18Q3.Rmd

  # Cell line lineage
  plot_lin <- ggplot(data = gene, aes(x = lineage_name, y = Score, color = Mutation_Status)) +
    geom_point(alpha = 0.5) +
    scale_color_manual(values = crispr_color) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    scale_y_continuous(sec.axis = sec_axis(~ .)) +
    coord_flip() +
    theme(legend.position = "none") +
    labs(y = "CERES Score", x = "Cell Line Lineage",
         color = "Mutation Status", title = g)

  # Arrange plots
  plot <- ggarrange(ggarrange(plot_lin, nrow = 1, labels = c("A")),
                    ggarrange(plot_mut, plot_cn, plot_ge, nrow = 3,
                              labels = c("B", "C", "D"), heights = c(2, 3, 3)),
                    font.label = list(size = 30, face = "bold"),
                    nrow = 1, ncol = 2, widths = c(3, 2))
  return(plot)
}
```

@@

### Make individual heatmaps per cluster

Take in a sorted gene list from a larger heatmap and produce smaller, individual heatmaps:
```{r, eval=FALSE}
makeHeatmaps <- function(clust_obj, clust_num) {
  chm_plot_cols <- colnames(clust_obj)
  chm_plot_rows <- rownames(clust_obj)

  chm_plot <- Heatmap(clust_obj, name = "CERES Score",
          bottom_annotation = HeatmapAnnotation(df = chm_annot),
          bottom_annotation_height = unit(5, "in"),
          row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
          col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
          na_col = "black",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          show_column_names = FALSE,
          row_title_gp = gpar(fontsize = 60, fontface = "bold"),
          show_row_names = FALSE,
          row_dend_reorder = TRUE,
          column_dend_reorder = TRUE,
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          column_dend_height = unit(4, "in"),
          row_dend_width = unit(4, "in"),
          width = 3)

  chm_ge_plot <- Heatmap(chm_ge[row_order(chm_scores_draw)[[clust_num]],], name = "Gene Expression (RPKM)",
          col = colorRamp2(c(min(chm_ge[!is.na(chm_ge)]), 0.25, max(chm_ge[!is.na(chm_ge)])), c("dodgerblue4", "white", "firebrick4")),
          na_col = "black",
          cluster_rows = FALSE, cluster_columns = FALSE,
          show_row_names = FALSE, show_column_names = FALSE,
          column_title = "Gene Expression",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          width = 1)
  chm_cn_plot <- Heatmap(chm_cn[row_order(chm_scores_draw)[[clust_num]],], name = "Copy Number",
          col = colorRamp2(c(min(chm_cn[!is.na(chm_cn)]), 2, max(chm_cn[!is.na(chm_cn)])), c("dodgerblue4", "white", "firebrick4")),
          na_col = "black",
          cluster_rows = FALSE, cluster_columns = FALSE,
          show_row_names = FALSE, show_column_names = FALSE,
          column_title = "Copy Number",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          width = 1)
  chm_mut_plot <- Heatmap(chm_mut[row_order(chm_scores_draw)[[clust_num]],], name = "Mutation Status",
          na_col = "black",
          col = c("cyan3", "darkorchid"),
          cluster_rows = FALSE, cluster_columns = FALSE,
          show_row_names = FALSE, show_column_names = FALSE,
          column_title = "Mutation Status",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          width = 1)

  chm_all_plot <- chm_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot

  pdf(paste0("./plots_18Q3/crispr_heatmap_clustered/crispr_heatmap_all_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
  draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()

  pdf(paste0("./plots_18Q3/crispr_heatmap_ge_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
  draw(chm_plot + chm_ge_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()

  pdf(paste0("./plots_18Q3/crispr_heatmap_mut_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
  draw(chm_plot + chm_mut_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()

  pdf(paste0("./plots_18Q3/crispr_heatmap_cn_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
  draw(chm_plot + chm_cn_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()
}
```

@@

@@

ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 5, device = "pdf")
```

@@

```{r, eval=FALSE}
crispr_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif <- adj_signif(crispr_signif)
crispr_signif <- crispr_signif[order(crispr_signif$p),]
saveRDS(crispr_signif, "./data_munging/rds/crispr_signif.rds")
```

@@

@@

```{r, eval=FALSE}
crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")
```

@@

```{r, eval=FALSE}
crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")
```

@@

@@

```{r}
shrna_signif <- readRDS("./data_munging/rds/shrna_signif.rds")

@@

# Mutation status
chm_mut_grid <- merge(crispr_grid, maf_df[, c("Broad_ID", "Hugo_Symbol", "Mutation_Status")], by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
chm_mut_grid$Mutation_Status <- ifelse(is.na(chm_mut_grid$Mutation_Status), 0, 1)
chm_mut <- reshape(chm_mut_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
chm_mut_rows <- chm_mut$Hugo_Symbol
chm_mut$Hugo_Symbol <- NULL
chm_mut_cols <- colnames(chm_mut) %>% gsub("Mutation_Status.", "", .)
chm_mut <- matrix(as.numeric(unlist(chm_mut)), nrow = nrow(chm_mut))
rownames(chm_mut) <- chm_mut_rows
colnames(chm_mut) <- chm_mut_cols
saveRDS(chm_mut, "./data_munging/rds/crispr_heatmap_mut.rds")

@@

### K-means clustered

Code for k-means clustered heatmap:
```{r, eval=FALSE}
chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_column_names = FALSE,
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_row_names = FALSE,
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3,
        km = 5, gap = unit(0.5, "in"))

chm_scores_draw <- draw(chm_scores_plot, heatmap_legend_side = "right", annotation_legend_side = "right")

pdf("./plots_18Q3/crispr_heatmap_euclidean_split5.pdf", width = 100, height = 100, paper = "special")
chm_scores_draw
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()

chm_scores_c1 <- chm_scores[row_order(chm_scores_draw)[[1]],]
chm_scores_c2 <- chm_scores[row_order(chm_scores_draw)[[2]],]
chm_scores_c3 <- chm_scores[row_order(chm_scores_draw)[[3]],]
chm_scores_c4 <- chm_scores[row_order(chm_scores_draw)[[4]],]
chm_scores_c5 <- chm_scores[row_order(chm_scores_draw)[[5]],]

makeHeatmaps(chm_scores_c1, 1)
makeHeatmaps(chm_scores_c2, 2)
makeHeatmaps(chm_scores_c3, 3)
makeHeatmaps(chm_scores_c4, 4)
makeHeatmaps(chm_scores_c5, 5)
```

@@

```{r}
colnames(chm_annot)
```

@@

chm_annot_list <- HeatmapAnnotation(df = chm_annot,annotation_legend_param = list(Primary_Disease = list(nrow = 6, title = "Primary Disease", title_position = "topleft"), Primary_Tissue = list(nrow = 6, title = "Primary_Tissue", title_position = "topleft"), Culture_Type = list(nrow = 6, title = "Culture Type", title_position = "topleft"), Source = list(nrow = 6, title = "Source", title_position = "topleft")))

chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
        bottom_annotation = chm_annot_list,
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        row_names_gp = gpar(fontsize = 10),
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_names_gp = gpar(fontsize = 8),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

@@

chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        row_names_gp = gpar(fontsize = 10),
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_names_gp = gpar(fontsize = 8),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "pearson",
        clustering_distance_columns = "pearson",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

>>>>

  # Cell line lineage
  plot_tissue <- ggplot(data = gene, aes(x = primary_tissue, y = Score, color = Mutation_Status)) +
    geom_point(alpha = 0.5) +
    scale_color_manual(values = crispr_color) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    scale_y_continuous(sec.axis = sec_axis(~ .)) +
    coord_flip() +
    theme(legend.position = "none") +
    labs(y = "CERES Score", x = "Primary Tissue",
         color = "Mutation Status", title = g)

  # Arrange plots
  plot <- ggarrange(ggarrange(plot_tissue, nrow = 1, labels = c("A")),
                    ggarrange(plot_mut, plot_cn, plot_ge, nrow = 3,
                              labels = c("B", "C", "D"), heights = c(2, 3, 3)),
                    font.label = list(size = 30, face = "bold"),
                    nrow = 1, ncol = 2, widths = c(3, 2))
  return(plot)
}
```

@@

@@

## Scores

Distribution of scores across cell lines and primary tissues. Each data point represents a single cell line.
```{r fig.height=4, fig.width=12}
ceres_summ <- crispr_data %>% group_by(primary_tissue) %>% summarize(Max = max(Score),
                                                                     Min = min(Score))
score_summ_plot <- ggplot(data = crispr_data, aes(x = primary_tissue, color = primary_tissue)) +
  geom_boxplot(mapping = aes(y = Score), outlier.shape = NA) +
  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Min)) +
  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Max)) +
  scale_y_continuous(breaks = seq(-4, 6, by = 1), labels = seq(-4, 6, by = 1)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
  labs(x = "Primary Tissue", y = "CERES Score")

# ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
```

@@

# ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
```

@@

```{r, eval=FALSE}
crispr_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif <- adj_signif(crispr_signif)
crispr_signif <- crispr_signif[order(crispr_signif$p),]
saveRDS(crispr_signif, "./data_munging/rds/crispr_signif.rds")

write.table(crispr_signif, file = "~/Desktop/crispr_signif_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r fig.height=3, fig.width=6}
wilcox_gene_plot <- ggplot(data = crispr_signif, aes(x = p.adj)) +
  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslategray3", color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 4500)) +
  scale_y_continuous(breaks = seq(0, 4500, by = 500), labels = formatC(seq(0, 4500, by = 500), format = "d")) +
  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")

ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 10, height = 5, device = "pdf")
```

@@

```{r, eval=FALSE}
crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")

write.table(crispr_signif_lineage, file = "~/Desktop/crispr_signif_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=FALSE}
crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")

write.table(crispr_signif_tissue, file = "~/Desktop/crispr_signif_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r fig.height=3, fig.width=6}
wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue, aes(x = p.adj)) +
  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslateblue", color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 55000)) +
  scale_y_continuous(breaks = seq(0, 55000, by = 5000), labels = formatC(seq(0, 55000, by = 5000), format = "d")) +
  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")

ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 10, height = 5, device = "pdf")
```

@@

```{r, eval=FALSE}
shrna_signif <- readRDS("./data_munging/rds/shrna_signif.rds")

@@

# Mutation status
chm_mut_grid <- merge(crispr_grid, maf_df[, c("Broad_ID", "Hugo_Symbol", "Mutation_Status")], by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
chm_mut_grid$Mutation_Status <- ifelse(is.na(chm_mut_grid$Mutation_Status), "Other", chm_mut_grid$Mutation_Status)
chm_mut_grid$Mutation_Status <- ifelse(chm_mut_grid$Mutation_Status == "Other", 0, 1)
chm_mut <- reshape(chm_mut_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
chm_mut_rows <- chm_mut$Hugo_Symbol
chm_mut$Hugo_Symbol <- NULL
chm_mut_cols <- colnames(chm_mut) %>% gsub("Mutation_Status.", "", .)
chm_mut <- matrix(as.numeric(unlist(chm_mut)), nrow = nrow(chm_mut))
rownames(chm_mut) <- chm_mut_rows
colnames(chm_mut) <- chm_mut_cols
saveRDS(chm_mut, "./data_munging/rds/crispr_heatmap_mut.rds")

@@

### All genes, no omics

```{r, eval=FALSE}
chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))

chm_all_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = chm_annot_list,
        bottom_annotation_height = unit(5, "in"),
        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
        row_title = "Genes", column_title = "Cancer Cell Lines",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
        row_names_gp = gpar(fontsize = 5),
        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
        column_names_gp = gpar(fontsize = 5),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(2, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

pdf("./plots_18Q3/crispr_heatmap_euclidean_all.pdf", width = 50, height = 50, paper = "special")
draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
dev.off()
```

@@

@@

chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))

chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
        bottom_annotation = chm_annot_list,
        bottom_annotation_height = unit(5, "in"),
        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
        row_title = "Genes", column_title = "Cancer Cell Lines",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
        row_names_gp = gpar(fontsize = 5),
        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
        column_names_gp = gpar(fontsize = 5),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(2, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

@@

chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))
